---
title: Lalín
author: ''
date: '2018-11-08'
slug: lalín
categories: ["territorio e urbanismo"]
tags: ["poboacion","rural","demografia"]
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo=F,comment = NA, tidy = FALSE, warning = FALSE, message = FALSE)
source(here::here("content","02_scripts/mapa_nomen17.R"))
```

This is a minimal example of how to use [htmlwidgets](http://www.htmlwidgets.org/index.html) in R Markdown posts. We will use a tidy version of Anscombe's quartet (thanks to [David Robinson](https://rpubs.com/dgrtwo/tidy-anscombe)). To reshape the anscombe dataset, you will need the **dplyr** and **tidyr** packages loaded. You'll also need to install and load the **DT** package for example 1, and the **ggplot2** and **plotly** packages for example 2.

#Introdución

Neste primeiro escrito imos falar do problema da gran cantidade de defuncións en comparacion relativa coa de nacementos que están arrastrando á poboación lalinense ao avellentamento desaforado e que provocará, no futuro, unha dificultade para manter a categoría do municipio.

```{r mapa interactivo}
mapa_interactivo
```

